Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/abstract.tex

JavaScript is a very popular programming language today. Several
engine implementations compete for market dominance. Although a
specification document and an conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. One reason for the difficulty in implementing correct
engines stems from the fact that the specification is intentionally
incomplete and evolves frequently.

This paper reports on a study we ran to evaluate the importance of
diversity to find functional bugs in JavaScript engines. For that, we used two
simple diversity-aware techniques--test transplantation and cross-engine
differential testing. The first technique\Comment{Test transplantation} evaluates the effects of
running test suites of a given engine in another engine. The second technique\Comment{Cross-engine
differential testing} evaluates the effects of fuzzing existing inputs
and then comparing the output produced by different engines with a
differential oracle.

>>>>

JavaScript is a very popular programming language today with several
engine implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the specification is intentionally
incomplete and evolves frequently.

This paper reports on a study we ran to evaluate the importance of
diversity to find functional bugs in JavaScript engines. For that, we use two
simple diversity-aware techniques--test transplantation and cross-engine
differential testing. The first technique\Comment{Test transplantation} evaluates the effects of
running test suites of a given engine in another engine. The second technique\Comment{Cross-engine
differential testing} evaluates the effects of fuzzing existing inputs
and then comparing the output produced by different engines with a
differential oracle.

### 2018-08-24 paper/paper.tex

JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,business-insider,stackify}, with
penetration in various segments including, web development, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification
and implementations. It is natural to expect that such improvements
lead to sensible changes in engine implementation. In fact, even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those
bugs. It\Comment{Finding bugs in \js\ engines} is also
challenging. For example, a test that passes in one engine could
legitimately fail in a different engine because of some undefined
behavior in the spec. These cases of undefined behavior can be
localized by searching for the string ``implementation-dependent'' in
the ES6 spec document~\cite{ecmas262-spec}. As another example, a test
may fail because the engine does not fully implement some feature. The
publicly-available Kangax compatibility table~\cite{kangax} relates
\js\ features with the engines that support them. To sum, it is often
non-trivial to assess if a test fails because of a bug or because of
some other reason making test automation more challenging. Developing
reliable engines is difficult because specifications are intentionally
incomplete as to enable flexibility during development and because
they evolve frequently.

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} evaluates the
ability of leveraging diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that \Fix{...}

>>>>

% ,business-insider
JavaScript (\js{}) is one of the most popular programming languages
today~\cite{redmonk-javascript,stackify} with
penetration in various software development segments including, web, mobile,
and, more recently, the Internet of
Things~(IoT)~\cite{simply-technologies}. The interest of the community
for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
lead to sensible changes in engine implementations~\cite{kangax}. Even small
changes can have high practical impact. For example, in October 2014 a
new attribute added to Array objects resulted in the MS Outlook
Calendar web app, which is built in \js{}, failing under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

Finding bugs in \js\ engines is an important problem given the range
of applications that could be affected with those bugs. It is also
challenging.  Specifications are intentionally incomplete as to enable
development flexibility. In addition, they evolve frequently to
accomodate the pressing demands from
developers~\cite{ecmas262-spec-repo}. An official conformance test
suites exist for \js~\cite{tc39-github}, but, naturally, many test
scenarios are not covered in the suite. In addition, we noticed that a
significant fraction (5 to 15\%) of the tests constantly fail on the
most popular engines, reflecting the struggle of developers in keeping
up with the pace of spec evolution (see Table~\ref{tab:test262}).

%% WHAT WE DID
This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on JavaScript engines. We evaluated
effectiveness of two complementary diversity-aware testing
techniques. \emph{Test transplantation} leverages diversity of test
cases to find bugs. It evaluates the effects that running \js{} test
files from a given engine have in detecting bugs in other engines. The
intuition is that developers design test cases with different
objectives in mind. Replaying these tests, written for a given engine,
in a different engine may reveal unanticipated
problems. \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
bugs. More precisely, this technique fuzzes existing test
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. The
intuition is that similar inputs to those already tested may reveal
problems. Our study measures the ability of these techniques in
finding bugs and the impact of false positives, which
can arise in both testing scenarios.
